### 2022-11-29 abstract.tex
added paper 4

The fact that a scientific finding can be replicated in an independent
replication study is central to its credibility. However, various large-scale
replication failures have shown that the replicability of scientific findings is
often lower than expected. This ``replication crisis'' has led to several
methodological reforms in the past decade, an increased conduct of replication
studies being one of them. Yet despite this rise of replication research, there
is no consensus on which statistical methods should be used for the design and
analysis of replication studies; Various methods already exist and various new
ones have been proposed in response to the crisis. This thesis centres around a
proposal based on the reverse-Bayes approach. The key idea is to reverse the
traditional ``forward'' use of Bayes' theorem (``prior + likelihood
$\rightarrow$ posterior''), starting instead with a pre-specified posterior and
deducing the corresponding prior (``posterior + likelihood $\rightarrow$
prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% setting as it enables the mathematical formalization of scepticism regarding the
% finding from the original study.
This allows us to challenge the original finding by determining a sceptical
prior for the underlying effect size such that the resulting posterior is no
longer convincing. This prior then represents the position of a sceptic who
remains unconvinced by the original study. Whether or not the sceptics' position
is justified can then be assessed in light of the new data from the replication
study. The larger the conflict between the replication data and the sceptic, the
larger the degree of replication success. This procedure can be summarized in a
single quantitative measure of replication success, termed the sceptical
$p$-value.

The first and largest part of the thesis consists of extending this procedure. A
first extension replaces tail probabilities by Bayes factors as measures of
evidence. The sceptical prior is now determined such that the original finding
is no longer convincing in terms of a Bayes factor. In contrast to tail
probabilities, Bayes factors have a more natural interpretation and allow for
direct quantification of evidence for one hypothesis versus another. As with the
sceptical $p$-value, the procedure leads to a single measure quantifying the
degree of replication success called the sceptical Bayes factor. A second
extensions recalibrates the original procedure to produce more appropriate
inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The third extension provides a
framework for Bayesian design of replication studies. This framework allows for
combining the data from the original study with external knowledge, which leads
to potentially more efficient designs compared to classical approaches.

The second part of the thesis is concerned with reverse-Bayes approaches in
general. The reverse-Bayes idea was first proposed in the 1950s, but it has
mostly been forgotten. To increase awareness and show potential use cases,
reverse-Bayes history and methods are summarized in a comprehensive review.
Furthermore, a short commentary on a recently proposed reverse-Bayes method
draws connections to other reverse-Bayes methods.

>>>>

The credibility of a scientific finding is based on the fact that it can be
replicated when the same study is repeated with new subjects. However, various
failures to replicate major scientific findings in the social and life sciences
indicate that replicability is often lower than expected. This ``replication
crisis'' has led to several methodological reforms in the past decade, an
increased conduct of replication studies being one of them. Yet despite this
increase in replication studies, there is no consensus on a fundamental
question: How should replication success be defined statistically?
% Various methods already exist and various new ones have
% been proposed in response to the crisis. This thesis centres around a proposal
% based on the reverse-Bayes approach. The key idea is to reverse the traditional
% ``forward'' use of Bayes' theorem (``prior + likelihood $\rightarrow$
% posterior''), starting instead with a pre-specified posterior and deducing the
% corresponding prior (``posterior + likelihood $\rightarrow$
% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% % setting as it enables the mathematical formalization of scepticism regarding the
% % finding from the original study.
% This allows us to challenge the original finding by determining a sceptical
% prior for the underlying effect size such that the resulting posterior is no
% longer convincing. This prior then represents the position of a sceptic who
% remains unconvinced by the original study. Whether or not the sceptics' position
% is justified can then be assessed in light of the new data from the replication
% study. The larger the conflict between the replication data and the sceptic, the
% larger the degree of replication success. This procedure can be summarized in a
% single quantitative measure of replication success, termed the sceptical
% $p$-value.

The first and largest part of this thesis extends a recently proposed
reverse-Bayes method for quantifying replication success. The key idea is to
challenge the finding from the original study with a sceptical prior so that the
resulting posterior provides no longer evidence for the finding from the study.
While the original proposal defined evidence through tail probabilities, the
extension developed here replaces them with Bayes
factors. % The sceptical prior is now
% determined such that the original finding is no longer convincing in terms of a
% Bayes factor. In contrast to tail probabilities,
We find that the extended method combines two notions of replicability: It
ensures that original and replication study independently provide evidence for
an effect while also ensuring that their effect estimates are compatible.
Compared to the original method, the extension also avoids a statistical paradox
which the original method suffered from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The second extensions recalibrates the original procedure to produce more
appropriate inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The recalibrated procedure has good
frequentist properties comparable to the standard method used in practice. The
third extension provides a framework for Bayesian design of replication studies
which allows for combining the data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and it can potentially lead to more efficient designs
compared to classical approaches that cannot take it into account.

The second part of the thesis is concerned with reverse-Bayes approaches in
general. The reverse-Bayes idea was first proposed in the 1950s, but it has
mostly been forgotten. To increase awareness and show potential use cases,
reverse-Bayes history and methods are summarized in a comprehensive review. The
review includes also some new results on connections between revere-Bayes
methods and meta-analysis. Finally, a commentary paper on a recently proposed
reverse-Bayes method draws connections to other reverse-Bayes methods.
